\documentclass[letterpaper]{article}
\usepackage{aaai24}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage[hyphens]{url}
\usepackage{booktabs}
\usepackage{natbib}

\title{Short Questions 1}
\author{
    Josh Manchester\\
    Department of Computer Science\\
    University of Colorado Colorado Springs\\
    Colorado Springs, CO 80918\\
    \texttt{jmanches@uccs.edu}
}

\begin{document}

\maketitle

\section*{Question 1}
\textit{What is reinforcement learning? Compare it briefly with supervised and unsupervised learning.}

\vspace{0.5em}

Sutton and Barto describe reinforcement learning (RL) as ``a third machine learning paradigm, alongside supervised learning and unsupervised learning'' \citep{sutton2018reinforcement}. In supervised learning, a human labels data ahead of time, telling the system the ``right answer'' for each example \citep{morales2020grokking}. Unsupervised learning finds hidden patterns in unlabeled data without any feedback. RL is different: an agent takes actions in an environment, receives rewards as feedback, and learns a policy to maximize cumulative reward over time. The key distinction is that RL feedback is delayed and there is no teacher providing correct answers---only better or worse outcomes. An RL agent must also balance \textit{exploration} of new actions with \textit{exploitation} of known good ones, a tradeoff that ``does not even arise in supervised and unsupervised learning'' \citep{sutton2018reinforcement}.

\section*{Question 2}
\textit{What are at least five publication venues where you are likely to find recently authored high-quality papers on reinforcement learning?}

\vspace{0.5em}

Finding quality research means knowing where to look. Based on Google Scholar's H5-index rankings for artificial intelligence, five top venues for reinforcement learning papers are: (1)~\textbf{ICML}, the International Conference on Machine Learning (H5:~272), which publishes foundational work on RL theory and algorithms; (2)~\textbf{AAAI}, the Association for the Advancement of Artificial Intelligence conference (H5:~232), covering RL applications in planning and robotics; (3)~\textbf{IEEE Transactions on Neural Networks and Learning Systems} (H5:~165), a high-impact journal for neural network-based RL research; (4)~\textbf{IJCAI}, the International Joint Conference on Artificial Intelligence (H5:~136), the oldest AI conference (established 1969) with broad RL coverage; and (5)~the \textbf{Journal of Machine Learning Research} (H5:~130), a respected open-access journal that has published seminal RL algorithms. These venues consistently feature cutting-edge reinforcement learning research and are recognized by the research community as top-tier outlets.

\section*{AI Use Statement}

Claude (Anthropic) was used to format my answers in AAAI LaTeX format and to retrieve H5-index rankings from Google Scholar Metrics.

\bibliography{references}

\end{document}
